% cv-us.tex
% $Id: anand_resume.tex,v 1.5 2007-12-31 22:21:04 ajoshi Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}
%\documentclass{llncs}
\usepackage{ifpdf}
\usepackage{amsmath}
\usepackage{multicol}
\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Anand A. Joshi},
  pdfcreator={$ $Id: anand_resume.tex,v 1.5 2007-12-31 22:21:04 ajoshi Exp $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={}
}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\Large\textbf}

%---------------------------------------------------------------------------

\name{Anand A. Joshi}

\begin{resume}

\section{CONTACT INFORMATION}
\begin{ncolumn}{2} Anand A. Joshi, \\
  Research Assistant Professor,& {\tt ajoshi@usc.edu}\\
  Signal \& Image Processing Institute,       & Phone: +1 (213) 284-4971 \\
  University of Southern California,& {\tt \verb+http://sipi.usc.edu/~ajoshi+} \\
  University Park Campus,\\
  EEB 426, M/C 2564, \\
  Los Angeles, CA 90089-2564               & 
\end{ncolumn}




\section{\bf EDUCATION}

{\bf University of Southern California, Los Angeles (2002-2008)}\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Electrical Engineering, August 2008, \textbf{GPA 4.0}\\
Specialization: Signal and Image Processing
\begin{list2}
%\vspace*{.05in}
\item Dissertation Topic: Geometric Methods for Image Registration and Analysis
\item Advisor: Richard M. Leahy
\end{list2}
\item[] M.A.~in Mathematics, May 2006, \textbf{GPA 4.0}\\
Specialization: Geometry
\begin{list2}
\item Thesis Topic: Harmonic Maps Between Riemannian Manifolds
\item Advisor: Francis Bonahon
\end{list2}
\end{list1}

{\bf Indian Institute of Technology, Kanpur (1999-2000)}\\
\vspace*{-.1in}
\begin{list1}
\item[] M.Tech.~in Electrical Engineering, May 2000, \textbf{GPA 9.75}
\begin{list2}
\item Thesis Topic: 2D and 3D image segmentation using level sets
\item Advisor: Govind Sharma
\end{list2}
\end{list1}

{\bf Shivaji University (1993-1997)}\\ 
\vspace*{-.1in}
\begin{list1}
\item[] B.E.~in Electronics, May 1997, \textbf{Graduated with Distinction}
\begin{list2}
\item Thesis Topic: Speaker Verification System using Spectral Analysis
\item Advisor: S D Apte
\end{list2}
\end{list1}

%
%\section{\bf RESEARCH EXPERIENCE}
%Registration and analysis of neuro-imaging data presents a challenging
%problem due to the complex folding patterns in the human brain.
%Specifically, the cortical surface of the human brain can be modeled as
%a highly convoluted 2D surface. Since it is non-flat, the non-euclidean
%geometry of the cortex needs to be accounted for while performing
%registration and subsequent signal processing of anatomical and
%functional signals on the cortex. Techniques from differential geometry
%offer a powerful set of tools to deal with the convoluted nature of the
%cortex. We present a method based on p-harmonic mapping for performing
%cortical surface parameterization. A 2D coordinate system induced by the
%flat mapping is then used to compute the surface metric and discretize
%derivatives in the surface geometry. For performing inter-subject
%cortical registration based on sulcal landmarks, we generalize
%thin-plate splines to non-flat surfaces by using covariant derivatives.
%We also present an FEM based method for simultaneous parameterization
%and registration of sulcal landmarks based on elastic energy
%minimization. These can be used to bring surface signals from individual
%brains to a common atlas surface. Isotropic and anisotropic diffusion
%filtering methods are formulated for processing of the cortical data.
%When the surface data is a point-set on the cortex, we propose a method
%to quantify its mean and variance with respect to the surface geometry.
%The registration techniques presented for surface alignment are then
%extended to volumes to perform full surface and volume registration.
%This is done by using volumetric harmonic mappings that extend the
%surface point correspondence to the cortical brain volume. Finally, the
%volumetric registration is refined by using inverse-consistent linear
%elastic intensity registration. This set of methods presents a unified
%framework for registration and analysis of the brain signals for
%inter-subject neuroanatomical studies.

%\newpage


%---------------------------------------------------------------------------

\section{\bf PROFESSIONAL EXPERIENCE}

\begin{itemize}
\item (2012-present) Research Assistant Professor, Signal and Image Processing Institute, University of Southern California. 
\item (2011) Post Doctoral Associate at Signal and Image Processing Institute (SIPI), University of Southern California, Los Angeles.
\item (2008-2010) Post Doctoral Scholar at Laboratory of Neuro Imaging (LONI), Univ. of Cal. Los Angeles (UCLA).
\item (Fall 2002-2008) Research Assistant (RA) at University of Southern California, Los Angeles.
\item (Fall 2005) Teaching Assistant, EE583 (Advance Filtering Theory), University of Southern California, Los Angeles.
\item (Sp 2004) Teaching Assistant, EE563 (Estimation Theory), University of Southern California, Los Angeles.
\item (Sp. 2003, Fall 2003) Teaching Assistant, EE464 (Probability Theory), University of Southern California, Los Angeles.
\item (2002) Senior Software Engineer at \textbf{SASKEN Ltd.}, Bangalore.
\item (2000-2002) Software Engineer at \textbf{SASKEN Ltd.}, Bangalore.
\item (Sp. 2000) Teaching Assistant, DSP, IIT Kanpur.
\item (1998) Engineering executive-marketing in \textbf{SIEMENS Ltd}, Mumbai.
\end{itemize}
\section{\bf ACADEMIC SERVICE}
\subsection{Journal Reviewing}
    \begin{multicols}{2}
    \begin{itemize}
\item IEEE Transactions on Medical Imaging,
\item IEEE Transactions on Biomedical Imaging,
\item IEEE Transactions on Image Processing,
\item SIAM Journal on Imaging Sciences,
\item IEEE Journal of Biomedical and Health Informatics,
\item IEEE Transactions on Biomedical Imaging,
\item Journal of Magnetic Resonance Imaging,
\item NeuroImage,
\item Medical Image Analysis,
\item International Journal of Biomedical Imaging
\item Journal of Neuroscience Methods
\item Human Brain Mapping, 
\item Nature Neuroscience,
\item Brain Connectivity
\item Pattern Recognition, Elsevier,
\item International Journal of Speech Technology,
\item Archives of General Psychiatry,
\item PLOS One
\item Optics Express
\item Frontiers in Neuroscience
\end{itemize}
\end{multicols}
\subsection{Conference Reviewing}
    \begin{multicols}{2}
    \begin{itemize}

\item IEEE International Symposium on Biomedical Imaging (ISBI),
\item IEEE Engineering in Medicine and Biology Conference (EMBC),
\item International Conference on Information Processing in Medical Imaging (IPMI),
\item Medical Image Computing and Computer Assisted Intervention (MICCAI),
\item Organization for Human Brain Mapping Annual Meeting (OHBM),
\item International Society for Magnetic Resonance in Medicine Annual Meeting and Exhibition (ISMRM),
\item Computer Vision and Pattern Recognition (CVPR),
\item Workshop in Biomedical Image Registration (WBIR),
\item SPIE Medical Imaging,
\item SPIE Image Processing,
\end{itemize}
\end{multicols}

\subsection{Grant, Books Reviews and other Services}
%    \begin{multicols}{2}
    \begin{itemize}
\item Judge for ECE Ming Hsieh research festival in EE, USC, 2019,
\item Served as a grant reviewer on NIH BDMA grant review panel, 2018.
\item Grant Review committee Clinical and Translational Science Institute (CTSI), 2012-current.
\item Book reviewer for Cambridge University Press,
\item Book reviewer for Wiley,
\item Judge for Ming Hsieh research festival in EE, USC, 2018,
\item Session Chair at Medical Image Computing and Computer Assisted Intervention (MICCAI), 2014,
\item Senior member, IEEE, 
\item OHBM member,

\end{itemize}
%\end{multicols}
\section{\bf TEACHING}
\begin{itemize}
\item \textbf{Instructor,} EE575: Computational Differential Geometry for Engineers, Spring 2016, offered in Spring 2020, \textbf{(Developed curriculum based on EE599 and taught the class)}. 
\item \textbf{Instructor,} EE599: Computational Differential Geometry for Engineers, Fall 2014, 2015, \textbf{(Developed curriculum and taught the class)}. 
\item \textbf{Guest Instructor,} EE599: Special Topics in Biomedical Imaging, Fall 2014. 
\item \textbf{Teaching Assistant,} EE583: Advance Filtering Theory, Fall 2005. Conducted weekly televised discussion sessions. 
\item \textbf{Teaching Assistant,} EE563: Advanced Filtering Theory, Spring 2004. 
\item \textbf{Teaching Assistant,} EE464: Advanced Filtering Theory, Spring 2002, 2003. Conducted weekly televised discussion sessions. 
\item \textbf{Directed Research,} Served as Directed Research mentor for $>20$ graduate students.

\end{itemize}

\section{\bf AWARDS AND HONORS}

\begin{itemize}
\item Google Research Credits worth $14,864$ in 2019.
\item NVIDIA GPU award 2018.
\item Cover page article in the journal NeuroImage 2011, (coauthor on the associated journal paper).
\item Featured tool, resource on NITRC (www.nitrc.org) (coauthor on the associated journal paper).
\item Featured paper on Medical Physics Web (medicalphysicsweb.org) (Joint first author). 
\item Featured article in the journal Physics in Medicine and Biology 2008 (Joint first author).
\item Academic achievement award (2008) for GPA 4.0 in EE and GPA 4.0 in Math by USC OIS.
\item Phi Kappa Phi Honors society (2008).
\item Deans fellowship for research related travel, USC 2007.
\item Travel awards at ISBI 2004 (first author) and ISBI 2007 (coauthor), ISBI 2008 (first author), ISBI 2009 (coauthor).
\item Best young investigated poster award at IPMI 2005.
\item Individual award for outstanding performance, smart project award and team award for outstanding quality by SASKEN Ltd. 2001.
\item National merit scholarship by Govt. of India 1993-1997.
\end{itemize}

\section{CONTRACT AND GRANT RESEARCH SUPPORT}

\subsection{Current Support}
Funding Agency: DoD CDMRP Epilepsy Research Program \\
Award Number: W81XWH-18-1-0614 \\
Title: Detecting Epileptogenic Anatomical and Functional Brain Changes
due to Traumatic Brain Injury in Veterans \\
Project Period: 8/30/2018 - 5/30/2021\\
Total cost: \$763,653\\
Project Role: PI\\
Effort: 3.6 calendar\\


Funding Agency:  National Institute of Neurological Diseases and Stroke\\
Award Number: R01 NS089212\\
Title: A Brain Atlas for Mapping Connectivity in Focal Epilepsy\\
Project Period: 3/1/2015 - 2/28/2020\\
Total Cost \$2,662,282 \\
Project Role: Co-I (PI: R. Leahy/JC Mosher)
Effort: 3.0 calendar\\

Funding Agency: National Institute of Biomedical Imaging and Bioengineering\\
Award Number: R01 EB026299 \\
Title: BrainStorm: Highly Extensible Software for Advanced Electrophysiology and MEG/EEG Imaging
Project Period: 06/15/2018 - 02/28/2022 \\
Total Cost:\$678,920 (2018)\\
Project Role: Co-I (PI: R. Leahy)\\
Effort: 2.4 calendar\\

Funding Agency: National Institute of Neurological Disorders and Stroke\\
Award Number: R01 NS074980 \\
Title: BrainSuite: Software for Analysis and Visualization of Multimodal Brain Imaging Data \\
Project Period: 05/01/2016 - 03/31/2022 \\
Total Cost: \$155,509 (2018) (USC subcontract) \\
Project Role: Co-I (PIs: Leahy/Shattuck)        \\                        
Effort: 2.4 calendar\\

\subsection{Previous Support}

Funding Agency: SC CTSI Pilot Funding: Multidisciplinary Resource Development\\
Title: Fully Automated Quantitative Adiposity Analysis Using MicroCT in Mouse Models\\
Project Period: 7/1/2013 - 6/30/14\\
Cost: \$35,194 \\
Project Role: Co-PI with Dr. Bing Bai\\

Funding Agency: National Institute of Neurological Disorders and Stroke\\
Award Number: R01 NS074980 \\
Title: Interactive Software for Semiautomated Analysis of Structural Brain  Images \\
Project Period: 05/01/2011 - 03/31/2016 \\
Total Cost: \$361,312 (USC subcontract) \\
Project Role: Co-I (PIs: Leahy/Shattuck) \\

\subsection{Pending Support}

Funding Agency: NIH - NINDS\\
Title: Mapping Brain Networks Involved in Post-traumatic Epilepsy using Diffusion MRI \\
Total Cost:  \$433,370 \\
Project Role: PI (joint with Bogdan P)\\

\newpage
\section{PUBLICATIONS}
\subsection{Journal Articles -  Published}
\begin{enumerate}

    \item  Choi SY, O'Neil SH, \textbf{Joshi AA}, Li J, Bush AM, Coates TD, Leahy RM, Wood JC, {Anemia predicts lower white matter volume and cognitive performance in sickle and non‐sickle cell anemia syndrome}, American Journal of Hematology, 2019.

    \item Foster BH, Shaw CB, Boutin RD, \textbf{Joshi AA}, Bayne CO, Szabo RM, Chaudhari AJ, {A principal component analysis-based framework for statistical modeling of bone displacement during wrist maneuvers}, {Journal of Biomechanics}, Vol 85, pp. 173-181, 2019.

    \item Tuvblad C, Niv S, Ashrafulla S, \textbf{Joshi AA}, Raine A, Leahy RM, Baker LA, {Relationships of Alpha, Beta, and Theta EEG Spectra Properties with Aggressive and Nonaggressive Antisocial Behavior in Children and Adolescents}, {American Journal of Psychology}, Vol. 131(4), pp. 429-437, 2018.

    \item \textbf{Joshi AA}, Chong M, Li J, Choi S, Leahy RM, {Are you thinking what I'm thinking? Synchronization of resting fMRI time-series across subjects}, {NeuroImage}, Vol 172, pp 740-752, 2018.

    \item Foster B, \textbf{Joshi AA}, Borgese M, Abdelhafez Y, Boutin RD, Chaudhari AJ, {WRIST: A WRist Image Segmentation Toolkit for carpal bone delineation from MRI}, Computerized Medical Imaging and Graphics 63, pp. 31-40, 2017.

    \item Choi S, Bush AM, Borzage MT, \textbf{Joshi AA}, Mack WJ, Coates TD, Leahy RM, Wood JC, {Hemoglobin and mean platelet volume predicts diffuse T1-MRI white matter volume decrease in sickle cell disease patients}, NeuroImage: Clinical, vol. 15, pp. 239-246. 

    \item Habibi A, Damasio A, Ilari B, Veiga R, \textbf{Joshi AA}, Leahy RM, Haldar JP, Varadarajan D, Bhushan C, Damasio H, Childhood Music Training Induces Change in Micro and Macroscopic Brain Structure: Results from a Longitudinal Study, Cerebral Cortex,  Vol 28 (12), pp. 4336-4347, 2017.

    \item Chong M, Bhushan C, \textbf{Joshi AA}, Choi S, Haldar JP, Shattuck DW, Spreng RN, Leahy RM, Individual parcellation of resting fMRI with a group functional connectivity prior, NeuroImage, 156, pp. 87-100, 2017. 

    \item Wang ZI, Krishnan B, Shattuck DW, Leahy RM, Moosa ANV, Wyllie E, Burgess RC, Al-Sharif NB, \textbf{Joshi AA}, Alexopoulos AV, Mosher JC, Udayasankar U, Jones SE, {Automated MRI Volumetric Analysis in Patients with Rasmussen Syndrome}, American Journal of Neuroradiology, 37(12), 2348-2355, 2016.

    \item Bhushan C, Chong M, Choi S, \textbf{Joshi AA}, Haldar JP, Damasio H, Leahy RM, {Temporal non-local means filtering reveals real-time whole-brain cortical interactions in resting fMRI}, PLoS One, (11) 7, 2016.

    \item Lederman C, \textbf{Joshi AA}, Dinov ID, Van Horn JD, Vese LA, Toga AW,,, {A Unified Variational Volume Registration Method Based on Automatically Learned Brain Structures}, Journal of Mathematical Imaging and Vision 55(2): 179-198, 2016.

    \item \textbf{Joshi AA}, Leahy RM, Badawi RD, Chaudhari AJ, {Registration-Based Morphometry for Shape Analysis of the Bones of the Human Wrist}, IEEE Trans. Med. Imaging 35(2): 416-426, 2016.

    \item Marusak HA, Furman DJ, Kuruvadi N, Shattuck DW, Joshi SH, \textbf{Joshi AA}, Etkin A, Thomason ME, {Amygdala responses to salient social cues vary with oxytocin receptor genotype in youth}, Neuropsychologia, Volume 79, Part A, Pages 1–9, 2015.

    \item Lederman C, \textbf{Joshi AA}, Dinov ID, Van Horn JD, Vese LA and Toga AW, {A Unified Variational Volume Registration Method Based on Automatically Learned Brain Structures}, Journal of Mathematical Imaging and Vision 2015 in press.

    \item Marusak HA, Kuruvadi N, Vila AM, Shattuck DW, Joshi S, \textbf{Joshi AA}, Jella PK, Thomason ME, {Interactive effects of BDNF Val66Met genotype and trauma on limbic brain anatomy in childhood}, European Child and Adolescent Psychiatry. in press 2015.

    \item Martinez K, Madsen SK, \textbf{Joshi AA}, Joshi SH, Roman FJ, Villalon-Reina J, Burgaleta M, Karama S, Janssen J, Marinetto E, Desco M, Thompson PM, Colom R, {Reproducibility of brain-cognition relationships using three cortical surface-based protocols: An exhaustive analysis based on cortical thickness}, Human Brain Mapping, Vol 36 (8), pp 3227–3245, 2015.

    \item Wei M, \textbf{Joshi AA}, Zhang M, Mei L, Manis FR, He Q, Beattie RL, Xue G, Shattuck DW, Leahy RM, Xue F, Houston SM, Chen C, Dong Q, Lu ZL, {How age of acquisition influences brain architecture in bilinguals}, Journal of Neurolinguistics, 36, 35-55, 2015. 

    \item Bhushan C, Haldar JP, Choi S, \textbf{Joshi AA}, Shattuck DW, Leahy RM, {Co-registration and distortion correction of diffusion and anatomical images based on inverse contrast normalization}, NeuroImage, 115, pp. 269-280.

    \item Shi J, Collignon O, Xu L, Wang G, Kang Y, Lepore F, Lao Y, \textbf{Joshi AA}, Lepore N, Wang Y, {Impact of early and late visual deprivation on the structure of the corpus callosum: A study Combining Thickness profile with Surface Tensor-based morphometry}, Journal Neuroinformatics, 2015 Jul;13(3):321-36.

    \item Chaudhari AJ, Leahy RM, Wisen BL, Lane NE, Badawi RD and \textbf{Joshi AA}, {Global point signature for shape analysis of carpal bones}, Physics in Medicine and Biology,  Phys. Med. Biol. 59 961, 2014

    \item Santos J., Chaudhari AJ, \textbf{Joshi AA}, Ferrero A., Yang K., Boone JM, Badawi RD, {Non-Rigid registration of serial dedicated breast CT, longitudinal dedicated breast CT and PET/CT images using the diffeomorphic demons method}, Physica Medica,30 (6), 713-717, 2014.

    \item Prasad G, \textbf{Joshi AA}, Feng A, Toga AW, Thompson PM, Terzopoulos D, {Skull-Stripping with Machine Learning Deformable Organisms},  Journal of Neuroscience Methods.  236, 114-124 2014.

    \item Habibi A, Ilari B, Crimi K, Metke M, Kaplan JT, \textbf{Joshi AA}, Leahy RM, Shattuck DW, Choi SY, Ficek B, Haldar JP, Damasio A, Damasio H, {An Equal Start: Absence of Group Differences in Cognitive, Social and Neural Measures Prior to Music or Sports Training in Children},  Frontiers in Human Neuroscience, 2014.

    \item Niv S, Ashrafulla S, Tuvblad C, \textbf{Joshi A}, Raine A, Leahy R, Baker LA, {Childhood EEG frontal alpha power as a predictor of adolescent antisocial behavior: A twin heritability study}, Biol Psychol. 2014 Nov 29. pii: S0301-0511(14)00251-8.

    \item Shi J, Collignon O, Xu L, Wang G, Kang Y, Lepore F, Lao Y, \textbf{Joshi A}, Lepore N, Wang Y,{Impact of early and late visual deprivation on the structure of the corpus callosum: A study Combining Thickness profile with Surface Tensor-based morphometry}, Journal Neuroinformatics, 2015 1-16.

    \item Bhushan C, \textbf{Joshi AA}, Leahy RM, Haldar JP, {Improved B0-distortion correction in diffusion MRI using interlaced 1-space sampling and constrained reconstruction}, Mag. Res. Med 72(5) 1218-1232 2014.

    \item Ashrafulla S, Haldar JP, \textbf{Joshi AA}, Leahy RM, {Canonical Granger Causality between Regions of Interest}, NeuroImage, 83, 189–199. 2013.

    \item \textbf{Joshi AA}, Hu H, Leahy RM, Toga AW, Nayak K, {Intra-subject registration and atlas-based segmentation of 3D human abdominal fat-water MRI}, Journal of Magnetic Resonance in Imaging,  37(2):423-430. February 2013.

    \item Yang Y, Raine A, \textbf{Joshi AA}, Joshi S, Chang YT, Schug RA, Wheland D, Leahy R, Narr KL, {Frontal information flow and connectivity in psychopathy}, Br J Psychiatry. 2012, Nov 201(5):408-9.

    \item Yang Y, \textbf{Joshi AA}, Joshi SH, Baker LA, Narr KL, Raine A, Thompson PM, Damasio H, {Genetic and Environmental Influences on Cortical Thickness among 14-Year-Old Twins}, NeuroReport, 2012 Aug 22;23(12):702-6.

    \item Joshi SH, Cabeen RP, \textbf{Joshi AA}, Sun B, Dinov I, Narr KL, Toga AW, Woods RP, {Diffeomorphic Sulcal Mapping on the Cortex}, IEEE Trans. on Med Imaging,  2012 Jun;31(6):1195-212.

    \item Thomason ME, Dennis EL, \textbf{Joshi AA}, Joshi SH, Dinov ID, Chang C, Henry ML, Johnson RF, Thompson PM, Toga AW, Glover GH, Van Horn JD, Gotlib IH, {Resting-state fMRI can reliably map neural networks in children}, NeuroImage 2011 Vol 55(1), pp. 165-75.

    \item Lederman C, \textbf{Joshi AA}, Dinov I, Vese L, Toga AW, Van Horn JD {The generation of tetrahedral mesh models for neuroanatomical MRI}, NeuroImage. 2011 Vol 55(1), pp. 153-164.  \textbf{[Featured on the journal cover page. Featured tool/resource on www.nitrc.org]}

    \item \textbf{Joshi AA}, Lepore N,Joshi SH, Lee AD, Barysheva M, Stein JL, McMahon KL, Johnson K, de Zubicaray GI, Martin NG, Wright MJ, Toga AW, Thompson PM, {The contribution of genes to cortical thickness and volume}, NeuroReport. 2011  22(3):101-105.

    \item Bernstein LE, Jiang J, Pantazis D, Lu ZL, \textbf{Joshi AA}, {Visual phonetic processing localized using speech and nonspeech face gestures in video and point-light displays}, Hum Brain Mapp. 2011 Oct;32(10):1660-76.

    \item Dutta J, Ahn S, \textbf{Joshi AA}, Leahy RM, {Illumination Pattern Optimization for Fluorescence Tomography}, Physics in Medicine and Biology. 2010; 55(10): 2961-82.

    \item Chaudhari AJ, Bowen SL, Burkett GW, Packard NJ, Godinez F, \textbf{Joshi AA}, Naguwa SM, Shelton DK, Hunter JC, Boone JM, Buonocore MH, Badawi RD. {High-resolution (18)F-FDG PET with MRI for monitoring response to treatment in rheumatoid arthritis}, Eur J Nucl Med Mol Imaging. 2010 May; 37(5): 1047.

    \item \textbf{Joshi AA}, Pantazis D, Li Q, Damasio H, Shattuck DW, Toga AW, Leahy RM, {Sulcal set optimization for cortical surface registration}, Neuroimage. 2010; 50(3):950-9.

    \item \textbf{Joshi AA}, Chaudhari AJ,  Li C, Dutta J, Cherry SR, Shattuck DW, Toga AW and Leahy RM {DigiWarp: a method for deformable mouse atlas warping to surface topographic data}, Phys Med Biol. 2010; 55(20):6197-214.

    \item Pantazis D, \textbf{Joshi AA}, Jiang J, Shattuck DW, Bernstein LE, Damasio H, Leahy RM, {Comparison of landmark-based and automatic methods for cortical surface registration}, Neuroimage. 2010; 49(3):2479-93.

    \item Chaudhari AJ, \textbf{Joshi AA}, Bowen SL, Leahy RM, Cherry SR and Badwai RD, {Spatial distortion correction and crystal identification for position-sensitive avalanche photodiode-based PET scanners}, IEEE Trans Nucl Sci. 2009; 56(3):549-556.

    \item Shattuck DW, \textbf{Joshi AA}, Pantazis D, Kan E, Dutton RA, Sowell ER, Thompson PM, Toga AW, Leahy RM, {Semi-automated method for delineation of landmarks on models of the cerebral cortex}, J Neurosci Methods. 2009; 178(2):385-92.

    \item Chaudhari AJ, \textbf{Joshi AA}, Bowen SL, Leahy RM, Cherry SR and Badwai RD, {Crystal identification in Positron Emission Tomography using nonrigid registration to a Fourier-based template}, Phys Med Biol. 2008; 53(18):5011-27. \textbf{[Featured article on medical physics web, Featured in Phys Med Biol.]}

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM, {A Parameterization-based Numerical Method for Isotropic and Anisotropic Diffusion Smoothing on Non-Flat Surfaces}, IEEE Trans Image Process. 2009; 18(6):1358-65.

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM {Surface-constrained volumetric brain registration using harmonic mappings}, IEEE Trans Med Imaging. 2007; 26(12):1657-69.
\end{enumerate}

%\subsection{Journal Papers - Accepted}
%\begin{enumerate}

% \item 
%\end{enumerate}

\subsection{Journal Papers - Submitted}
\begin{enumerate}
\item \textbf{Joshi AA}, Bhushan C, Salloum R, Wisnowski JL, Shattuck DW, Leahy RM, {An Anisotropic Laplace Equation Method for Cortical Thickness Measurement}, Medical Image Analysis, Invited Article, 2019.

\end{enumerate}

\subsection{Conference Proceedings - Published}
\begin{enumerate}

    \item \textbf{Joshi AA}, Akrami J, Li J, Leahy RM, {A matched filter decomposition of fMRI into resting and task components}, Proc. MICCAI, 2019, 673-681.

    \item Akrami H, \textbf{Joshi AA}, Li J, Leahy RM, {Group-wise alignment of resting fMRI in space and time}, {Proc. SPIE Medical Imaging 2019}: Image Processing, 10949, 109492W.

    \item Li J, Wisnowski JL, \textbf{Joshi AA}, Leahy RM, {Brain network identification in asynchronous task fMRI data using robust and scalable tensor decomposition}, {Proc. SPIE Medical Imaging 2019}: Image Processing, 10949, 109490N. 

    \item \textbf{Joshi AA}, Li J, Akrami H, Leahy RM, {Predicting cognitive scores from resting fMRI data and geometric features of the brain}, {Proc. SPIE 10949, Medical Imaging 2019}: Image Processing, 109492E, 2019.
    
    \item \textbf{Joshi AA}, Li J, Chong M, Akrami H, Leahy RM, {rfDemons: Resting fMRI-Based Cortical Surface Registration Using the BrainSync Transform}, Proc. MICCAI (3) 2018: 198-205

    \item \textbf{Joshi AA}, Bhushan C, Salloum R, Wisnowski JL, Shattuck DW, Leahy RM, {Using the Anisotropic Laplace Equation to Compute Cortical Thickness}, MICCAI (3) 2018: 549-556. 

    \item Li J, Choi S, \textbf{Joshi AA}, Wisnowski JL, Leahy RM: {Global PDF-based temporal non-local means filtering reveals individual differences in brain connectivity},  ISBI 2018: 15-19.

    \item \textbf{Joshi AA}, Choi S, Sonkar G, Chong M,  Gonzalez-Martinez J, Nair D, Shattuck DW,  Damasio H, Leahy RM, {A Whole Brain Atlas with Sub-parcellation of Cortical Gyri using Resting fMRI}, SPIE Medical Imaging, 101330O-101330O-9, 2017.

    \item Rajagopal G, Joshi AA, Leahy RM, {An Algorithm for Automatic Parameter Adjustment for Brain Extraction in BrainSuite},  SPIE Medical Imaging 101330K-101330K-10, 2017.

    \item \textbf{Joshi AA}, Chong M, Leahy RM, {BrainSync: An Orthogonal Transformation for Synchronization of fMRI Data Across Subjects}, Proc. MICCAI 2017, pp. 486-494.

    \item Awate SP, Leahy RM, \textbf{Joshi AA}, {Kernel Methods for Riemannian Analysis of Robust Descriptors of the Cerebral Cortex}, Proc. IPMI 2017, pp. 28-40.

    \item Shishegar R, \textbf{Joshi AA}, Tolcos M,  Walker DW, Johnston LA, Automatic segmentation of fetal brain using diffusion-weighted imaging cues, Proc. ISBI 2017, pp. 804-807.

    \item S Choi, AM Bush, M Borzage, A Joshi, TD Coates, R Leahy, JC Wood, {Hemoglobin Level and Platelet Size Predicts Grey and White Matter Volume Loss Measured By Tensor Based Morphology in Sickle Cell Disease}, Blood 2016 128:2481.

    \item Choi S, Bush AM, Borzage M, \textbf{Joshi AA}, Coates TD, Leahy RM, Wood JC, {Regional Susceptibility to Chronic Anemia in WM Microstructure Using Diffusion Tensor Imaging}, Blood, 128(22), 3640-3640. 

    \item Awate SP, Leahy RM, \textbf{Joshi AA}, {Riemannian statistical analysis of cortical geometry with robustness to partial homology and misalignment}, International Conference on Medical Image Computing and Computer-Assisted Intervention, 237-246, 2016.

    \item Chaudhari AJ, Foster BH, Noblett DA, Boutin RD, Szabo RM, Bayne CO, Leahy RM, Lane NE, \textbf{Joshi AA}, {Sex Differences in Morphometry of the Anatomical Structures of the First Carpometacarpal Joint}, Journal of Womens Health, 25(9), 960-960, 2016.

    \item Wang I, Krishnan B, Shattuck D, \textbf{Joshi A}, Leahy R, Alexopoulos A, Burgess R, Mosher J, Udayasankar U, Moosa A, Wyllie, E, Jones S. {Automated MRI Volumetric Analysis of Rasmussen's Encephalitis}, submited American Epilepsi Society Annual Meeting 2015.

    \item Chong M, \textbf{Joshi AA}, Haldar J, DuPre E, Luh WM, Shattuck DW, Spreng RN, Leahy RM, {A Group Approach to Functional Cortical Parcellation from Resting-State fMRI}, OHBM 2015.

    \item Varadarajan D, Wamg IZ, \textbf{Joshi A}, Shattuck D, Jones S, Leahy R. {Detecting Focal Cortical Dysplasia using Population-based Models of Cortical Thickness},  OHBM 2015

    \item Choi S, Bush A, Borzage M, \textbf{Joshi AA}, Rajagopalan V, Coloigner J, Lepore N, Coates TD and Wood JC, {Diffuse T1-MRI White Matter Volume Decrease in Patients with Sickle Cell Disease}, OHBM 2015.


    \item \textbf{Joshi AA}, Salloum R, Bhushan C, Leahy RM, {Measuring Asymmetric Interactions in Resting State Brain Networks, Information Processing in Medical Imaging}, 2015, 399-410.

    \item Jones S, Wang I, Alexopoulos A, Al-Sharif N, Burgess R, \textbf{Joshi A}, Krishnan B, Leahy R, Mosher J, Udayasankar U, Shattuck D, {Automated Quantitative Assessment of Rasmussen's Encephalitis}, ASNR 2015.

    \item Li H, El Fakhri G, \textbf{Joshi A}, Li Q, {An ADMM Reconstruction Algorithm for Joint Registration and Attenuation Correction in Transmission-Less Gated TOF PET}, IEEE Medical Imaging Conference, 2014.


    \item Joshi S, Woods R, \textbf{Joshi A}, Fears S, Al-Sharif N, Leahy R, Shattuck D, {A statistical toolbox for BrainSuite}, OHBM 2014.

    \item \textbf{Joshi A}, Bhushan C, Shattuck D, Leahy R, {Estimation of cortical thickness from T1-weighted MRI images using tissue fractions}, OHBM 2014.

    \item Martinez K, \textbf{Joshi A}, Madsen S, Joshi S, Karama S, Roman F, Villalon-Reina J, Burgaleta M, Thompson P, Colom R, {Reproducibility of Brain-Cognition Relationships Using Different Cortical Surface-Based Analysis Protocols}, Proc. ISBI 2014, in press.

    \item Eschenburg K, Villalon-Reina J, Jahanshad N, Nir T, Daianu M, \textbf{Joshi A}, Leonardo C, de Bode C, Bookheimer S, Salamon N, Thompson P, {Analysis of Structural Brain Connectivity in 6 Cases of Hemispherectomy},  Proc. ISBI 2014., in press.


    \item Bai B, \textbf{Joshi AA}, Longo VD, Conti PS and Leahy RM, {A Registration-based Segmentation Method with Application to Adiposity Analysis of Mice MicroCT Images}, SPIE Medical Imaging 2013, in press.

    \item \textbf{Joshi AA}, Ashrafulla S, Shattuck DW, Damasio H, Leahy RM, {Cortical Shape Analysis using the Anisotropic Global Point Signature}, MICCAI, MFCA workshop, 2013.
 
    \item \textbf{Joshi AA}, Leahy RM, Badawi R, Chaudhari AJ, {Morphometry for Early Monitoring of Treatment Response in Theumatoid Arthritis}, Proc IEEE Int Symp Biomed Imaging. 2013, 121–124. 

    \item Martinez K, Villalon J, Kessel D, \textbf{Joshi AA}, Pineda JA, Jahanshad N, Nir T, Eschenburg K, Roman FJ, Burgaleta M, Solana AB, Quiroga MA, Colom R, Thompson PM, {Explorator factor analysis of brain networks reveals sub-networks related to cognitive performance}, Proc. ISBI 2013, 608-611.

    \item Bhushan C, Haldar J, \textbf{Joshi AA}, Leahy RM, {Correcting Susceptibility-Induced Distortion in Diffusion-Weighted MRI using Constrained Nonrigid Registration}, APSIPA 2012. 

    \item \textbf{Joshi AA}, Ashrafulla S, Shattuck DW, Damasio H, Leahy RM, {An Invariant Shape Representation using the Anisotropic Helmholtz Equation}, Proc. MICCAI (3) 2012: 607-614.

    \item Somayajula S, \textbf{Joshi AA}, Leahy RM, {Non-rigid Image Registration Using Gaussian Mixture Models}, Proc. WBIR, LNCS Springer 2012, 286-295. 

    \item \textbf{Joshi AA}, Shattuck DW and Leahy RM, {A Fast and Accurate Method for Automated Cortical Surface Registration and Labeling}, Proc. WBIR LNCS Springer 2012, 180-189.

    \item \textbf{Joshi AA}, Shattuck D, Damasio H, Leahy RM, {Geodesic curvature flow on surfaces for automatic sulcal delineation}, Proc IEEE ISBI 2012, 430-433.

    \item Ashrafulla S, Haldar J, \textbf{Joshi AA}, Leahy RM, {Canonical Granger causality applied to functional brain data}, Proc. IEEE ISBI 2012, 1751-1754.

    \item Joshi SH, \textbf{Joshi AA}, Toga AW, McMahon K, de Zubicaray G, Martin N, Wright M, Thompson PM, {Genetic influences on sulcal patterns of the brain}, Proc. IEEE ISBI 2012, 414-417.

    \item Wheland D, \textbf{Joshi AA}, McMahon K, Hansell N, Martin N, Wright M, Thompson P, Shattuck DW, Leahy RM, {Robust identification of partial-correlation based networks with applications to cortical thickness data}, Proc IEEE ISBI 2012, 1551-1554.

    \item Prasad  G, \textbf{Joshi A}, Feng A, Barysheva M, McMahon K, de Zubicaray G, Martin N, Wright M, Toga AW, Terzopoulos D and Thompson PM, {Deformable Organisms and Error Learning for Brain Segmentation}, MICCAI MFCA 2011, 135-147.

    \item \textbf{Joshi AA}, Joshi SH, Thomason M, Dinov ID, Toga AW, {Evaluation of Connectivity Measures and Anatomical Features for Statistical Brain Networks}, Proc. IEEE ISBI 2011, 836-840. 

    \item Prasad G, \textbf{Joshi AA}, Thompson PM, Toga AW, Shattuck DW, Terzopoulos D, {Skull-stripping with Deformable Organism}, Proc. IEEE ISBI 2011, 1662-1665. 

    \item Jahanshad N, Aganj I, Lenglet C, \textbf{Joshi AA}, Jin Y, Barysheva M, McMahon K, de Zubicaray G, Martin N, Wright M, Toga A, Sapiro G, Thompson P, {Sex Differences in the Human Connectome: 4-Tesla High Angular Resolution Diffusion Imaging (HARDI) Tractography in 234 Young Adult Twins}, Proc. IEEE ISBI 2011, 939-943.

    \item Villalon J, \textbf{Joshi AA}, Toga AW, Thompson PM, {Comparison of Volumetric Registration Algorithms for Tensor-Based Morphometry}, Proc. IEEE ISBI 2011, 1536-1541. 

    \item Joshi SH, Cabeen R, Sun B, \textbf{Joshi AA}, Gutman B, Zamanyan A, Chakrapani S, Dinov I, Woods RP, Toga AW, {Cortical Sulcal Atlas Construction using a Diffeomorphic Mapping Approach}, Proc. of MICCAI. 2010; 13(Pt 1):357-366.

    \item Joshi SH, Cabeen R, \textbf{Joshi AA}, Narr K, Toga AW, {Diffeomorphic Sulcal Shape Analysis for Cortical Surface Registration}, Proc. CVPR 2010; 475-482.

    \item Lederman C, \textbf{Joshi AA}, Van Horn JD, Vese L, Toga A, {Robust Tetrahedral Mesh Generation for Medical Images using Active Surfaces}, Proc. ISBI 2010; 436-439.

    \item \textbf{Joshi AA}, Joshi SH, Dinov I, Shattuck DW, Leahy RM, Toga AW, {Anatomical Structural Network Analysis of Human Brain using Partial Correlation of Gray Matter Volumes}, Proc. of ISBI. 2010; 844-847.

    \item \textbf{Joshi AA}, Lepore N, Joshi SH, Lee AD, Barysheva M, de Zubicaray GI, Wright MJ, McMahon KL, Toga AW, Thompson PM, {Genetic Analysis of Cortical Thickness in 372 twins}, Proc. ISBI 2010; 101-104.

    \item \textbf{Joshi AA}, Joshi SH, Leahy RM, Shattuck DW, Dinov I, Toga AW, {Bayesian approach for network modeling of brain structural features}, Proc. SPIE. 2010; Vol. 7626, 762607.

    \item Dutta J, Ahn S, \textbf{Joshi AA} and Leahy RM, {Optimal Illumination Patterns for Fluorescence Tomography}, Proc. IEEE ISBI 2009, 1275-1278.

    \item \textbf{Joshi AA}, Chaudhari AJ, Shattuck DW, Dutta J, Leahy RM and Toga AW, {Posture Matching and Elastic Registration of a Mouse Atlas to Surface Topography Range Data}, Proc. ISBI 2009, 366-369.

    \item \textbf{Joshi AA}, Leahy RM, Toga AW, Shattuck DW, {A Framework for Brain Registration via Simultaneous Surface and Volume Flow}, Proc. IPMI 2009; 21:576-88.

    \item \textbf{Joshi AA}, Pantazis D, Damasio H, Li Q, Shattuck DW, Bernstein LE and Leahy RM, {Optimization of Landmark Selection for Cortical Surface Registration}, CVPR 2009, 699-706. 

    \item Chaudhari AJ, \textbf{Joshi AA}, Yibao Wu, Leahy RM, Cherry SR and Badawi RD, {Spatial distortion correction and crystal identification for position-sensitive avalanche photodiode-based PET scanners}, Nuclear Science Symposium Conference. 2009; 19-25,5045-5052.

    \item Somayajula S., \textbf{Joshi AA}  and Leahy RM, {Mutual Information Based Non-Rigid Mouse Registration Using a  Scale-space Approach}, Proc. of ISBI. 2008; pp 1147-1150. 

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM, {Brain Image Registration using Cortically Constrained Harmonic Mappings}, Proc. IPMI 2007; 4584,359-371.

    \item Eckstein I, \textbf{Joshi AA}, Leahy RM. Deshbrun M. {Generalized Surface Flows for Deformable Registration and Cortical Matching}, Proc. of MICCAI. 2007; 692-700.

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Richard M. Leahy {Simultaneous Surface and Volumetric Brain Registration Using Harmonic Maps}, Proc. SPIE, Vol. 6498, 2007; 649816.

    \item Chaudhari AJ , \textbf{Joshi AA}, Darvas F and Leahy RM, {A method for atlas-based volumetric registration with surface constraints for Optical Bioluminescence Tomography in small animal imaging}, Proc. SPIE 2007; 6510; 651024.

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Richard M. Leahy (2007) {A finite element method for elastic parameterization and alignment of cortical surfaces using sulcal constraints, Biomedical Imaging}, Proc. of ISBI 2007; 640-643. 

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM, {Registration of cortical surfaces using sulcal landmarks for group analysis of MEG data}, International Congress Series Volume 1300, New Frontiers in Biomagnetism. Proceedings of the 15th International Conference on Biomagnetism 2007; 229-232.

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM, {A Framework for Registration, Statistical Characterization and Classification of Cortically Constrained Functional Imaging Data}, Proc. IPMI 2005;  186-196,

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM, {Cortical surface parameterization by p-harmonic energy minimization}, Proc. of ISBI 2004; 428-431.
\end{enumerate}

%\subsection{Conference Proceedings - Accepted}
%\begin{enumerate}
%\end{enumerate}

\subsection{Conference Abstracts - Published}
\begin{enumerate}

    \item Taylor K, \textbf{Joshi AA}, Leahy RM, Mosher JC, Nair DR, Combined RMS/Permutation test in cortico-cortical evoked potentials Labeling and Location Validation, American Epilepsy Society, Annual meeting, Baltimore, 2019.

    \item Akrami H, \textbf{Joshi AA}, Jian Li, Leahy RM, {TBI Lesion Detection Using a Variational Autoencoder}, American Epilepsy Society, Annual meeting, Baltimore, 2019.

    \item Choi S, O'Neil SH, Joshi AA, Miao X, Li J, Haldar JP, Coates T, Leahy RM, and Wood JC, {Exploring Anemia’s Impact on Brain Microstructure, Volume, Functional Connectivity, Iron and Cognitive Performance}, ASH Annual Meeting, 2019.

    \item Foster B, Shaw C, Boutin R, Szabo R, Bayne C, \textbf{Joshi AA}, Chaudhari AJ, {Real-time MRI-based Carpal Motion Assessment Using Statistical Displacement And Shape Models}, Orthopaedic Research Society Annual Meeting, Phoenix, Arizona, 2020.

    \item \textbf{Joshi AA}, Choi S, Shattuck DW, Leahy RM, {A method for automatic demarcation of sulcal and gyral regions on the cortical surface}, OHBM 2019. (also software demo).

    \item \textbf{Joshi AA}, Akrami H, Li J, Leahy RM, {A Matched Filter Decomposition of Task fMRI for Extraction of Dynamical Components}, OHBM 2019.

    \item Choi S, \textbf{Joshi AA}, Vu C, Li J, O'Niel S, Wood J, Leahy RM, {Alterations of brain connectivity inanemic subjects using fMRI under hypoxic and hyperoxic states}, OHBM 2019.

    \item Almarhabi A, \textbf{Joshi AA}, Aydore S, {Fast Detection of Brains with Abnormalities Using Recursive Agglomerative Clustering}, OHBM 2019.

    \item Taylor KN, Nair DR, Gonzalez-Martinez J, Leahy RM, \textbf{Joshi AA}, Mosher JC, {Automated Invasive Electrode Labeling and Location Validation}, AES 2018. 

    \item Chaudhari AJ, Foster B, Szabo RM, Boutin RD, Bayne CO, Boone JM, Ma KL, Badawi RD, Lane NE, Leahy RM, Crisco JJ, \textbf{Joshi AA}, {Probabilistic Atlas of the First Carpometacarpal Joint}, Proceedings of the 3 rd ITOW, Stanford University, Stanford, CA, USA, 2018.

    \item Quachtran B, \textbf{Joshi AA}, Bhushan C, Leahy RM, Shattuck D, {Combined T1-Diffusion MRI Registration}, OHBM 2018.

    \item Akrami H, \textbf{Joshi AA}, Li J, Leahy RM, {Average template for comparison of resting fMRI based on group synchronization of their time series}, OHBM 2018.

    \item \textbf{Joshi AA}, McCoy D, Chong M, Li J, Choi S, Shattuck DW, Leahy RM, {BFP: A BrainSuite fMRI Pipeline}, OHBM 2018.

    \item Li J, Wisnowski JL, \textbf{Joshi AA}, Leahy RM, {Identifying Brain Networks Using Tensor Decomposition of Multiple Subject Asynchronous Task fMRI}, OHBM 2018.

    \item Chong M, \textbf{Joshi AA}, Leahy RM, {A New Feature Reduction Method for Improving High Dimensional Brain Connectivity Estimates}, OHBM 2018.

    \item Chaudhari AJ, Foster B, Szabo RM, Boutin RD, Bayne CO, Boone JM, Ma KL, Badawi RD, Lane NE, Leahy RM, Crisco JJ, \textbf{Joshi AA}, {Probabilistic Atlas of the First Carpometacarpal Joint}, Proceedings of the 3rd ITOW, 2018.

    \item Choi S, O'Neil S, \textbf{Joshi AA}, Bush A, Borzage M, Coloigner J, Coates T, Wood J, Leahy RM, {The Anemic Brain: Hemoglobin Level Predicts Brain Volume in Watershed areas and Cognitive function}, OHBM 2017.

    \item \textbf{Joshi AA}, Choi S, Chong M, Sonkar G, Gonzalez-Martinez G, Nair D, Shattuck D,  Damasio H, Leahy RM, {USCBrain Atlas: A Volumetric and Surface Atlas Delineated by Anatomical and Functional MRI}, OHBM 2017.

    \item Li J, \textbf{Joshi AA}, Choi S, Leahy RM, {Global PDF-based Non-Local means Filtering of Resting fMRI data}, OHBM 2017.

    \item \textbf{Joshi AA}, Chong M, Leahy RM, {Synchronization of fMRI Data Across Subjects and Scans by Orthogonal Transformation}, OHBM 2017.

    \item Joshi S, Kim Y, \textbf{Joshi AA}, Leahy RM,  Shattuck D, {Reproducible TBM and ROI Analyses Using the BrainSuite Statistics Toolbox (BSS)}, OHBM 2017.

    \item \textbf{Joshi AA}, Salloum R, Bhushan C, Leahy RM, {Measuring Asymmetric Connectivity in the Default Mode Network}, OHBM 2015.

    \item Chaudhari AJ, \textbf{Joshi AA}, Leahy RM, Wise BL, Lane NE, Badawi RD and Buonocore MH, {Thumb carpometacarpal joint motion and bone shape differences by sex}, Proceedings of the 1st International Thumb Osteoarthritis Workshop, Newport, Rhode Island, USA October 25-26, 2013.

    \item Chaudhari AJ, \textbf{Joshi AA}, Leahy RM, Lane NE, Badawi RD and Buonocore MH, {Sex-based imaging biomarkers of carpal bone motion and shape in Hand Osteoarthritis}, NIH Office of Research on Women's Health Tenth Annual Interdisciplinary Women's Health Research Symposium, Bethesda, MD, Oct 24-25, 2013.

    \item Beroukhim D, Konersman M, Chong M, \textbf{Joshi AA}, Bhusan C, Shattuck DW, Haldar JP, Leahy RM, Winstein CJ, {Effects of rehbilitation post-stroke: DTI analysis of corticospinal tract characteristics using BrainSuite13}, Society of Neuroscience 2013.

    \item Aydore S, Ashrafulla S, \textbf{Joshi AA}, Leahy RM, {A Measure of Connectivity in the Presence of Crosstalk}, IEEE ASILOMAR Conference on Signals, Systems and Computers, 2013.

    \item Xu L, Collignon O, Wang G, Kang Y, Lepore F, Shi J, Lao Y, \textbf{Joshi AA}, Lepore N, Wang Y, {Combining Thickness Information with Surface Tensor-based Morphometry for the 3D Statistical Analysis of the Corpus Callosum}, MICCAI, MFCA workshop 2013.

    \item Choi S, Bhushan C, \textbf{Joshi AA}, Raphel K, Tranel D, Shattuck DW, Haldar JP, Leahy RM, Damasio H, Wisnowski JL, {Altered orbitofrontal tissue microstructure in patients with chronic anterior temporal lobe lesions}, OHBM 2013.

    \item Shattuck DW, \textbf{Joshi AA}, Haldar J, Bhushan C, Choi S, Krause A, Wisnowski J, Damasio H, Toga A, Leahy RM, {New BrainSuite13 Tools for Image Segmentation, Registration , Connectivity Analysis and Visualization}, OHBM 2013.

    \item \textbf{Joshi AA}, Ashrafulla S, Shattuck DW, Damasio H, Leahy RM, {Automated Analysis of the Shape of Sulcal Curves using the Anisotropic Helmholtz Equation}, OHBM 2013.

    \item Eschenburg K, Villalon-Reina J, Nir T, \textbf{Joshi AA}, Terashima K, Jones M, Salamon N, de Bode S, Thompson PM, {A Preliminary Graph Theory Analysis of 5 Hemispherectomized Children}, OHBM 2013.

    \item Shattuck DW, \textbf{Joshi AA}, Haldar JP, Bhushan C, Choi S, Krause AC, Wisnowski JL, Toga AW and Leahy RM, {Tools for Brain Image Segmentation, Registration, and Connectivity Analysis}, ISMRM 2013. 

    \item Bhushan C, \textbf{Joshi AA}, Leahy RM, Justin Haldar, Accelerating Data Acquisition for Reversed-Gradient Distortion Correction in Diffusion MRI: A Constrained Reconstruction Approach, ISMRM 2013. [Magna Cum Laude Merit Award, Trainee Educational Stipend].

    \item Choi S, \textbf{Joshi AA}, Chitresh Bhushan, David W Shattuck, Richard M Leahy, Hanna Damasio, Ashok Panigrahy and Jessica L Wisnowski, A Multimodal Investigation of Neuronal/Axonal Integrity Using Structural T1-weighted Imaging, Diffusion Tensor Imaging, and H1 MR Spectroscopy, ISMRM 2013.

    \item Yang Y, Wang P, Baker LA, Damasio H, \textbf{Joshi AA}, Joshi SH, Narr KL, Raine A and Thompson PM, {Abnormal cortical thickness associates with psychopathic traits in adolescents}, Society for Neuroscience Annual Meeting October 13-17, 2012, in New Orleans, LA.

    \item Chaudhari AJ, \textbf{Joshi AA}, Leahy RM, Boutin RD, Wise RL, Lane NE, Badawi RD, Buonocore MH, {Sex-based imaging biomarkers of function in Hand Osteoarthritis}, BIRCWH Annual Meeting 2013.

    \item Beroukhim D, Konersman M, Chong M, \textbf{Joshi AA}, Bhusan C, Shattuck DW, Haldar JP, Leahy RM, Winstein CJ, {Effects of rehabilitation post-stroke: DTI analysis of corticospinal tract characteristics using BrainSuite13}, Society for Neuroscience 2013.

    \item Ma K, Qin Y, Liu Y, Reddy N, {Joshi AA}, Amezcua L, Lerner A, Shiroishi M, Liu B, {Knowledge discovery of potential disease patterns in multiple sclerosis lesions across imaging studies of diverse ethnicities}, RSNA 2013.

    \item Ashrafulla S, Haldar JP, \textbf{Joshi AA}, Leahy RM, {Canonical Granger Causality}, Biomag 2012.

    \item Martinez K, Roman FJ, \textbf{Joshi AA}, Abad FJ, Villalon J, Burgaleta M, Privado J, Escorial S, Shih PC, Quiroga MA, Alvarez-Linera J, Karama S, Haier R, Thompson PM and Colom R, {Imaging-derived gray matter measurements of the cerebral cortex and intelligence: A latent variable analysis of the P-FIT model}, ISIR 2012.

    \item \textbf{Joshi AA}, Shattuck DW and Leahy RM, {Refinement of Automated Cortical Surface Registration and Labelling using Gradient Curvature Flow}, Organization for Human Brain Mapping, Beijing, China, June 10-14, 2012.

    \item Villalon Reina J, Jahanshad N, \textbf{Joshi AA}, McMahon KL, de Zubicaray GI, Wright MJ, Toga AW, Leahy RM, Thompson PM, {How do cortical thickness profiles depend on thalamic connectivity?}, Organization for Human Brain Mapping, Beijing, China, June 10-14, 2012.

    \item Joshi SH, \textbf{Joshi AA}, Toga AW, McMahon KL, de Zubicaray GI, Martin NG, Wright MJ and Thompson PM. {Sulcal Shape Heritability on the Cortex}, Organization for Human Brain Mapping, Beijing, China, June 10-14, 2012.

    \item Yang Y, Wang P, Baker LA, \textbf{Joshi AA}, Joshi SH, Narr KL, Raine A and Thompson PM, {Thinner Temporal Cortex Identified in Adolescents with Increasing Psychopathy over Time}, Organization for Human Brain Mapping, Beijing, China, June 10-14, 2012.

    \item Yang Y, Wang P, Baker LA, \textbf{Joshi AA}, Joshi S, Narr KL, Raine A and Thompson PM, {Variations in Frontal and Striatal Morphology Associate with Psychopathic Traits in Adolescents}, Organization for Human Brain Mapping, Beijing, China June 10-14, 2012.

    \item Zingg B, Hintiryan H, Gou L, Lee D, Ng Q, \textbf{Joshi A}, Yamashita S, Bota M, Swanson L, Toga A, and Dong H, {Toward a Mouse Connectome: A High-throughput Approach for the Characterization of Long-range Connectivity in the Mouse Brain}. Janelia farm Conference, 2011.

    \item Lee D, Ng Q, Yamashita S, \textbf{Joshi AA}, Lee B, C Mena, Toga, AW and Dong H, {iConnectome: An informatics infrastructure for the processing, visualization, and analysis for the mouse connectome project}. SFN 2011.

    \item B Zingg, H Hintiryan, L Gou, D Lee, Q Ng, \textbf{A Joshi}, S Yamashita, M. Bota, L Swanson, A Toga, and H Dong, {Toward a Mouse Connectome: A High-throughput Approach for the Characterization of Long-range Connectivity in the Mouse Brain}. SFN 2011.

    \item Santos J, \textbf{Joshi A}, Chaudhari A, Badawi R, {Assessment of the advanced 3D registration for the spatial normalization of cross-sectional and longitudinal high-resolution breast PET/CT images}, BCI 2011, hosted by SNM center for molecular imaging  2011.

    \item Zingg B, Gou L, Hintiryan H, Lee D, \textbf{Joshi AA}, Yamashita S, Ng Q, Lee BW, Mena C, Swanson LW, Toga AW and Dong H, {Toward a Mouse Connectome: A High-throughput Approach for the Characterization of Long-range Connectivity in the Mouse Brain}. UCLA Neurology science day 2011. [Mazz Prize]

    \item Lederman C, \textbf{Joshi AA}, Dinov ID, Chan K, Vese L, Toga A, van Horn J, {A Unified Variational Approach to Structural Brain Registration}, OHBM 2011.

    \item \textbf{Joshi AA}, Carl Lederman, Ivo Dinov, Shantanu Joshi, Arthur Toga, John Van Horn, {Tetrahedral Mesh-based Morphometry of Brain Surfaces and Volumes}, OHBM 2011.


    \item Joshi SH, Cabeen R, \textbf{Joshi AA}, Narr K, Toga AW, Diffeomorphic Sulcal Pattern Matching for Cortical Surface Registration OHBM 2010.

    \item Thomason ME, Dennis EL, \textbf{Joshi AA}, Joshi SH, Dinov ID, Henry ML, Johnson RF, Thompson PM, Toga AW, Gotlib IH, Resting Functional Connectivity: Pattern reliability and longitudinal changes in childhood, OHBM 2010.

    \item Lepore N, \textbf{Joshi AA}, Brun C, Toga AW, Thompson PM, Combined Surface/Volume Fluid Registration-Performance Evaluation using Brain MRIs from 342 Adults, OHBM 2010.

    \item \textbf{Joshi AA}, Lepore N, Joshi SH, Brun C, Toga AW, The Contribution of Genes to  Cortical Thickness and Volume in Young Adults, OHBM 2010.

    \item Brun C, \textbf{Joshi AA}, Lepore N, Joshi SH, Lee A, Thompson PM, Cortical measures and heritability in 326 identical and fraternal twins, OHBM 2010.

    \item \textbf{Joshi AA}, Hu HH, Goran MI, Leahy RM, Toga AW, Nayak KS, A Software Tool for Volume Registration and Atlas-Based Segmentation of Human Fat-Water MRI Data in Longitudinal Studies, ISMRM 2010.

    \item Pantazis D, \textbf{Joshi AA}, Jintao J, Shattuck DW, Bernstein LE, Damasio H, and Leahy RM, {Evaluating the accuracy of cortical registration using landmark-based and automatic methods}, OHBM 2009.

    \item Chaudhari AJ, \textbf{Joshi AA}, Toga AW, Leahy RM, Cherry SR and Badawi RD, {Atlas-based attenuation correction for small animal PET/MRI scanners}, IEEE Medical Imaging Conference, 2009.

    \item Li Q., Shin T, \textbf{Joshi AA} and Nayak K, {A Fast Simultaneous Estimation of MRI Image and Deformation Map in Cardiac Imaging}, ISMRM 2009. 

    \item Vidal CN, Fox GR, Ballinger AM, Allen J, Baker L, Raine A, Bruss J, \textbf{Joshi AA}, Leahy RM, Pantazis D, Shattuck DW, Zhuang J, Damasio H, {Genetic Influences on Language Cortices: Preliminary Results from a Volumetric Twin Study}, The Society for Neuroscience annual meeting, San Diego, Nov 2-7, 2007.

    \item Li Q., \textbf{Joshi AA} and Leahy RM, {A Registration Framework based on Harmonic Mapping for Inter-subject Comparisons in Small Animal {PET/CT} Imaging}, Nuclear Science Symposium and Medical Imaging Conference, 2007.

    \item Shattuck DW, \textbf{Joshi AA}, Leahy RM and Toga AW {Automated Parameterized Cortical Surface Models from MRI}, Human Brain Mapping June 2005, Toronto, CA. (2005).

    \item \textbf{Joshi AA}, Shattuck DW, Thompson PM and Leahy RM {Thin Plate Spline Registration in the Intrinsic Geometry of the Cortical Surface},  Human Brain Mapping, Toronto, CA. (2005).

    \item \textbf{Joshi AA} and Leahy RM, {Unique conformal maps},  Image analysis workshop at Los Alamos, Dec 2002. 
\end{enumerate}


\subsection{Book Chapter}
\begin{enumerate}
    \item \textbf{Joshi AA},  Registration. In: Spalletta G., Piras F., Gili T. (eds) Brain Morphometry. Neuromethods, vol 136. Humana Press, Springer Protocols, New York, NY, 2018.
\end{enumerate}


\subsection{Technical Reports}
\begin{enumerate}

    \item Akrami H, \textbf{Joshi AA}, Leahy RM, (2019), Robust Variational Autoencoder, arXiv:1905.09961.
    
    \item Lepore N, \textbf{Joshi AA}, Leahy RM, Brun CC, Chou YY, Pennec X, Lee AD, Barysheva M, de Zubicaray GI, Wright MJ, McMahon KL, Toga AW, Thompson PM (2009). Surface and Volume Registration of Brain Magnetic Resonance Images, 4D Technical Report, April 2009.

    \item Lederman C, \textbf{Joshi AA}, Dinov I, Van Horn JD, Chan K, Vese L, Toga AW, Automatic Structural Brain Registration Using Finite Elements and Active Surfaces, UCLA Computational and Applied Mathematics Reports, December 2010. 

\end{enumerate}


\subsection{Thesis Work}
\begin{enumerate}
    \item \textbf{Joshi AA}, Geometric Methods for Image Registration and Analysis, PhD Dissertation, Ming Hseih Dept. Electrical Engineering, University of Southern California, Los Angeles, 2008.

    \item \textbf{Joshi AA}, Harmonic Maps Between Riemannian Manifolds, Masters Thesis, Dept. of Mathematics, University of Southern California, Los Angeles, 2006.

    \item \textbf{Joshi AA}, Shape Recovery in 2D, 3D Medical Images using Level Set Method, Masters Thesis, Dept. of Electrical Engineering, Indian Institute of Technology, 2000.

\end{enumerate}

\subsection{Talks and Presentations}
\begin{enumerate}

    \item \textbf{Joshi AA}, Robust Machine Learning for Brain Lesion Detection, CHLA, 2019. 

    \item \textbf{Joshi AA}, Predicting Cognitive Scores from Functional Imaging Data and Geometric Features of the Brain, SBMT 2019.

    \item \textbf{Joshi AA}, Are you thinking what I'm thinking? Synchronizing resting fMRI brain activity across subjects with BrainSync, Brain and Creativity Institute, USC, 2017.

    \item \textbf{Joshi AA}, Geometric techniques, PDEs and manifold learning for brain imaging. USC Mark and Mary Stevens
Neuroimaging and Informatics Institute, Keck School of Medicine of USC, 2017.

    \item \textbf{Joshi AA}, Brain Registration in BrainSuite, Childrens Hospital, Los Angeles, 2016.

    \item \textbf{Joshi AA}, BrainSuite-Brainstorm Training session USC University Park Campus, Los Angeles, October 2015.

    \item \textbf{Joshi AA}, BrainSuite – NeuroImaging Training Program 2015 UCLA Advanced Neuroimaging Summer Program, University of California, Los Angeles, August 2015.  

    \item \textbf{Joshi AA}, Geometric methods for bran image registration and signal analysis, Centro de Investigación en Matemáticas, 2012.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration and signal analysis, University of Southern California, Signal and Image Processing Institute, 2011.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration and signal analysis, University of California, Los Angeles, Dept. of Mathematics, Applied Math Colloquium, 2010.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration, University of California, Los Angeles, Image Processing Seminar, 2010. 

    \item \textbf{Joshi AA}, Geometric methods for brain image registration, University of North Carolina at Chapel Hill, 2010. 

    \item \textbf{Joshi AA}, Medical image registration and analysis, Workshop at Children's Hospital, Los Angeles, 2009.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration, SRI International, 2009. 

    \item \textbf{Joshi AA}, Medical image registration and analysis, DSP Experiments in MATLAB workshop at RSCOE, University of Pune, 2009.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration, University of California, Davis, 2008.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration and signal analysis, University of California, Los Angeles, LONI, CCB Presents, 2008.

    \item \textbf{Joshi AA}, Geometric methods for brain image registration and signal analysis, CSAIL, Massachusetts Institute of Technology, Biomedical Imaging and Analysis Seminar Series, 2008.

    \item \textbf{Joshi AA}, Simultaneous Surface and Volume Registration using Harmonic Maps, SIAM conference on Imaging Sciences, Minneapolis, 2006.
\end{enumerate}

\section{Open-Source Research Software Development}
\begin{itemize}
    \item Developed SVReg module in BrainSuite software. (\url{http://brainsuite.org/processing/svreg/})
    \item Contributed to BrainStorm by adding BrainSuite Compatibility.
    \item Automatic parameter tuning for Skull Extraction 
    \item Developed BrainSuite fMRI pipeline (\url{http://brainsuite.org/bfp/})
    \item Bone Shape Analysis software
    \item DigiWarp: Mouse registration (\url{https://github.com/ajoshiusc/digiwarp})
\end{itemize}

\section{Professional Software Development}
\begin{itemize}
    \item Embedded software development (C++ and assembly programming) of MPEG4 video decoder on Texas Instrument TMS 420 and ARM chipsets for SASKEN Ltd. The software was purchased by SAMSUNG for their mobile phones. 
    \item Microsoft video encoder and decoder for Texas Instrument chips.
    \end{itemize}

\section{Other Professional Activities}
\begin{itemize} 
    \item Developed Inventory Control flow at Siemens. I was responsible for import order, inventory control and deliveries of the MicroMaster and MiniMaster DC drives.
    \item Worked on pricing and marketing of MicroMaster and MiniMaster Drives for Siemens Mumbai.
\end{itemize}

\section{Research Software Training}
\begin{itemize}
\item  Speaker, BrainSuite Training @ USC, September 2013.
\item Speaker, BrainSuite Training @ UCLA, November 2013.
\end{itemize}

%------------------------------------------------------------------------------

%%===========================================================================%%
%\newpage
%\opening


%%---------------------------------------------------------------------------%%

%\begin{center}
%\vspace{\fill}\ \newline
%{\tiny \rm $ $RCSfile: anand\_resume.tex,v $ $ }
%{\tiny \rm $ $Date: 2007-12-31 22:21:04 $ $ }
%{\tiny \rm $ $Revision: 1.5 $ $ }
%\end{center}

\end{resume}

\end{document}

%%===========================================================================%%
\grid
